\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Online Appendix C -- Margins Plots} }

### 2018-12-10 Online Appendices/Appendix C.tex
Added Margins Plots

>>>>

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Margins/IdeoPlaceDem}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{Margins/LibPlaceDem}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Margins Plots for Place Interaction with Democracy}
	\label{Democracy}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Margins/IdeoPlaceAge}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{Margins/LibPlaceAge}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Margins Plots for Place Interaction with Regime Age}
	\label{Age}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Margins/IdeoPlaceFormula}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{Margins/LibPlaceFormula}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Margins Plots for Place Interaction with Electoral Formula}
	\label{Elect}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Margins/IdeoPlaceFree}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{Margins/LibPlaceFree}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Margins Plots for Place Interaction with Freedom House Ratings}
	\label{Freedom}
\end{figure}

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.475\textwidth}   
		\centering 
		\includegraphics[width=\textwidth]{Margins/IdeoPlaceCorrupt}
		\caption{Self-Placement Ideology}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.475\textwidth}
		\centering 
		\includegraphics[width=\textwidth]{Margins/LibPlaceCorrupt}
		\caption{Issue Stances}
	\end{subfigure}
	\caption{Margins Plots for Place Interaction with Corruption Perception Index Scores}
	\label{Corruption}
\end{figure}
